---
title: "R Notebook"
output: html_notebook
---
```{r}
# loading in libraries
library(tidyverse)
library(jsonlite)
```

```{r}
# loading in data
people <- read_csv("data/people.csv")
places <- read_csv("data/places.csv")
```

The problem / question:
Create a Docker image for outputting a summary of content in the database. You may implement this using a programming language of your choice.

The output must be in JSON format, and be written to a file in the data folder called data/summary_output.json. It should consist of a list of the countries, and a count of how many people were born in that country. We have supplied a sample output data/sample_output.json to compare your file against.

```{r}
# to be able to join the datasets, renaming place_of_birth on the people dataset
people <- people %>%
  rename(city = "place_of_birth")

# joining the tables, using an inner join to include all rows in both datasets
people_places <- people %>%
  inner_join(places, by = "city")
```

```{r}
# wrangling and making the total count
summary_people_places <- people_places %>%
  group_by(country) %>%
  count()
```

```{r}
write_json(summary_people_places, "data/summary_people.places.json", pretty = FALSE)
```

